Evaluating the Performance and Energy Efficiency of the COSMO-ART model system

### 2014-04-23 trunk/paper_enahpc14/paper.tex
shortens the paper's title
adds minor changes; updates paper.bib; includes references for related work
updates abstract

\title{Evaluating the Performance and Energy Efficiency of COSMO-ART,
  a Coupled Numerical Weather Forecast and Chemical Transport Model.}
%\thanks{}
%\subtitle{}

@@

\begin{abstract}
  In  this paper we  present the  energy-to-solution and  profiling of
  COSMO-ART on various  platforms.  This model is an  extension of the
  operational  weather forecast  model of  the German  weather service
  (DWD), developed for the  evaluation of the interactions of reactive
  gases  and aerosol  particles with  the state  of atmosphere  at the
  regional scale.  The overall  performance of this application on HPC
  systems is analysed  by a profiling study to  determine hotspots and
  identify  critical  CPU paths.   Moreover,  we describe  measurement
  devices and energy-aware techniques  employed to evaluate the energy
  footprint of the considered application and to get detailed insights
  about power bottlenecks.  Our motivation is to improve corresponding
  code    sections   to    sustain   performance    while   minimising
  energy-to-solution.   This  preliminary  work  sets  the  basis  for
  subsequent studies to tackle  challenges related to energy efficient
  high performance computing in the framework of the Exa2Green project
  (\url{http://exa2green.eu/}).

@@

\section{Related work}
\label{sec:1}
\input{Sec1:Related.tex}

@@

\section{Conclusion}
\label{concl}
\input{Conclusion.tex}

>>>>

\title{Evaluating the Performance and Energy Efficiency of the
  COSMO-ART model system}
%\thanks{}
%\subtitle{}

@@

\begin{abstract}
  In this  paper we investigate  the energy footprint  and performance
  profiling of COSMO-ART  on various HPC platforms.  This  model is an
  extension of  the operational weather  forecast model of  the German
  weather  service   (DWD),  developed  for  the   evaluation  of  the
  interactions of reactive gases  and aerosol particles with the state
  of atmosphere at the  regional scale.  Different measurement devices
  and energy-aware techniques are  described to evaluate both time and
  energy  to  solution  of  the  considered application  and  to  gain
  detailed  insights  into power  and  performance requirements.   Our
  motivation  is to  improve  corresponding code  sections to  sustain
  performance  while minimising energy-to-solution.   This preliminary
  work  sets the  basis for  subsequent studies  to  tackle challenges
  related  to  energy  efficient  high performance  computing  in  the
  framework of the Exa2Green project (\url{http://exa2green.eu/}).

@@

\section{Related work \emph{(to be completed)}}
\label{sec:1}
\input{Sec1:Related.tex}

@@

\section{Conclusion \emph{(to be completed)}}
\label{concl}
\input{Conclusion.tex}
